Human Factors Influencing Visual Statistical Inference

### 2017-10-19 submitted-v1/sociology_paper.Rnw
updated paper

\begin{table}[hbtp]
\caption{Demographic information of the subjects participating in the MTurk experiments. Average time taken for evaluating a lineup is shown in seconds.}
\centering
\scalebox{.85}{
\begin{tabular}{rlrrcr}
  \hline
  && \multicolumn{2}{c}{Participants}&Average& Number of\\
  \cline{3-4}
 Factor & Levels & Total &\% & Time & Responses \\ 
  \hline
Gender & Male & 1351 & 57.74 & 48.75 & 13542 \\ 
   & Female & 989 & 42.26 & 43.69 & 10538 \\ 
\hline
  Education & High school or less & 194 & 8.29 & 37.13 & 2253 \\ 
   & Under grad courses & 418 & 17.86 & 42.85 & 4068 \\ 
   & Under grad degree & 585 & 25.00 & 44.53 & 5792 \\ 
   & Graduate courses & 247 & 10.56 & 44.63 & 2471 \\ 
   & Graduate degree & 899 & 38.42 & 52.07 & 9496 \\ 
\hline
  Age & 18-25 & 743 & 31.75 & 43.50 & 7340 \\ 
   & 26-30 & 549 & 23.46 & 46.19 & 5610 \\ 
   & 31-35 & 375 & 16.03 & 44.19 & 3912 \\ 
   & 36-40 & 257 & 10.98 & 54.97 & 2714 \\ 
   & 41-45 & 140 & 5.98 & 43.89 & 1510 \\ 
   & 46-50 &  94 & 4.02 & 49.54 & 994 \\ 
   & above 50 & 184 & 7.86 & 52.32 & 2000 \\ 
\hline   
  Country & United States & 1086 & 46.41 & 39.65 & 10763 \\ 
   & India & 980 & 41.88 & 52.63 & 10238 \\ 
   & Rest of the world & 279 & 11.92 & 50.38 & 3079 \\

@@

@@

% latex table generated in R 3.2.2 by xtable 1.7-4 package
% Sun Aug 30 22:43:05 2015
\begin{table}[ht]
\caption{\label{tbl:anova_factor}Analysis of variance (ANOVA) table comparing full model, all the demographic factors, with the reduced models, obtained by removing respective factor variable. Gender does not have a significant effect on detection rate, but does on time to respond. All factors significantly affect time to respond.}
\centering
\scalebox{0.9}{
\begin{tabular}{lrrrrlrrrr}
& \multicolumn{4}{c} {Log Time (model~\ref{eqn:demographic_time})} & &\multicolumn{4}{c} {Detection rate (model~\ref{eqn:demographic_response})}  \\
\cline{2-5} \cline{7-10} 
 & Deviance & $\chi^2$ & df & $p$-value && Deviance & $\chi^2$ & df & $p$-value \\ \cline{2-5} \cline{7-10}
Full  & 51872.4 & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} &  & 23792.0 & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\ 
 - Age & 51329.3 & 543.2 & 6 & $<$0.001 & \hspace{0.5cm} & 23766.4 & 26.0 & 6 & $<$0.001 \\ 
 - Country & 51496.4 & 376.1 & 2 & $<$0.001 &  & 23765.9 & 26.0 & 2 & $<$0.001 \\ 
 - Degree & 51756.2 & 116.2 & 4 & $<$0.001 &  & 23768.2 & 23.8 & 4 & $<$0.001 \\ 
 - Gender & 51804.3 & 68.1 & 1 & $<$0.001 &  & 23789.7 & 2.2 & 1 & 0.140 \\ 
\cline{2-5} \cline{7-10}
\end{tabular}}
\end{table}

@@

% latex table generated in R 3.2.2 by xtable 1.7-4 package
% Sat Aug 29 14:17:22 2015
\begin{table}[hbtp]
\caption{\label{tbl:model_result_demographics}Parameter estimates of models~\eqref{eqn:demographic_time} and~\eqref{eqn:demographic_response} fitted for average log time taken and detection rate, respectively. For time taken all the demographic factors are significant. For detection rate, age group 36-40, rest of the world and graduate degree are significantly different. For gender no difference in performance is observed. Lineup variability is estimated to be very large for model~\eqref{eqn:demographic_response}.}
\centering
\scalebox{.9}{
\begin{tabular}{rrr>{( }r<{,}>{\hspace{-.1in}}l<{)}>{\hspace{-.15in}}l<{}cr>{( }r<{,}>{\hspace{-.1in}}l<{)}>{\hspace{-.15in}}l<{}}
 && \multicolumn{4}{c} {Log Time (model~\ref{eqn:demographic_time})} & &\multicolumn{4}{c} {Detection rate (model~\ref{eqn:demographic_response})}  \\

\cline{3-6} \cline{8-11} 
\multicolumn{2}{c}{{Demographic Factor} \hfill Level} & Est & 2.5\% & 97.5\% &   && Est & 2.5\% & 97.5\% &   \\ 
\cline{3-6} \cline{8-11}
\bf Fixed Effects & Average $\mu$ & 3.16 & 3.12 & 3.20 & *** &   & -0.61 & -0.79 & -0.43 & *** \\ [3pt]
\bf Age Category $(\alpha)$ & 18-25 & \multicolumn{5}{l}{0.00} & \multicolumn{4}{l}{\phantom{-}0.00} \\
&  26-30 & 0.06 & 0.03 & 0.08 & *** &   & 0.06 & -0.03 & 0.16 &  \\ 
&  31-35 & 0.07 & 0.04 & 0.10 & *** &   & 0.11 & 0.01 & 0.22 & * \\ 
&  36-40 & 0.23 & 0.20 & 0.26 & *** &   & 0.31 & 0.19 & 0.43 & *** \\ 
&  41-45 & 0.18 & 0.14 & 0.22 & *** &   & 0.16 & 0.00 & 0.31 & * \\ 
&  46-50 & 0.27 & 0.22 & 0.32 & *** &   & 0.14 & -0.05 & 0.33 &  \\ 
&  above 50 & 0.35 & 0.32 & 0.39 & *** &   & 0.15 & 0.01 & 0.28 & * \\ [3pt]
\bf Country $(\kappa)$& U.S. & \multicolumn{5}{l}{0.00} & \multicolumn{4}{l}{\phantom{-}0.00} \\
&  India & 0.23 & 0.21 & 0.25 & *** &   & -0.18 & -0.27 & -0.10 & *** \\ 
&  Rest of the world & 0.14 & 0.11 & 0.17 & *** &   & 0.08 & -0.04 & 0.20 &  \\ [3pt]
\bf Education $(\tau)$& High School & \multicolumn{5}{l}{0.00} & \multicolumn{4}{l}{\phantom{-}0.00} \\
&  Under grad courses & 0.13 & 0.09 & 0.16 & *** &   & -0.03 & -0.18 & 0.11 &  \\ 
&  Under grad degree & 0.13 & 0.10 & 0.17 & *** &   & 0.12 & -0.01 & 0.26 & . \\ 
&  Graduate courses & 0.01 & -0.04 & 0.05 &  &   & -0.17 & -0.33 & -0.01 & * \\ 
&  Graduate degree & 0.13 & 0.09 & 0.16 & *** &   & -0.06 & -0.19 & 0.07 &  \\ [3pt]
\bf Gender $(\gamma)$& Female & \multicolumn{5}{l}{0.00} & \multicolumn{4}{l}{\phantom{-}0.00} \\
&  Male & 0.08 & 0.06 & 0.10 & *** &   & 0.06 & -0.02 & 0.13 &  \\
\cline{3-6} \cline{8-11}
\bf Random Effects &  lineup $(\sigma_\ell)$& \multicolumn{5}{l}{0.29} & \multicolumn{4}{l}{\phantom{-}2.29} \\ 
                   &  Error $(\sigma)$& \multicolumn{5}{l}{0.69} & \multicolumn{4}{l}{\phantom{-}0.89}  \\ 
\cline{3-6} \cline{8-11}\\
\hline
\multicolumn{10}{l}{Signif. codes:  *** $<$ 0.001 $\le$ ** $<$ 0.01 $\le$ * $<$ 0.05 $\le$ . $<$ 0.1 $\le$ ` ' $<$ 1}
\end{tabular}}
\end{table}

@@

Figure~\ref{fig:demographic_effect} supports the model results. The average time taken to respond (natural log) and detection rate are computed by lineup for the different demographic factor levels, and displayed using boxplots. Mean values are shown as dots inside the boxplot, as this statistic rather than the median is used in the models. %There are some small differences across demographic groups. The youngest age group (18-25) took least average time to evaluate a lineup. People from India took more time than others. People who have only a high school degree took less time and this is related to what we have seen for young age group. Averages of log time taken by male and female participants look similar but there are some differences as we see in Table~\ref{tbl:demographics}. 
The means and medians for response time (top row) are essentially equal. There are some differences between the two in the detection rate plots (bottom row). The differences in these values for different factors, that was tested by the models, can be seen in the plots. However, particularly for detection rate, the variation is huge. A large component of the variation is difficulty of the lineup. In some lineups the actual data plot was distinctively different from the null plots, and we would expect that the detection rate would be close to 100\%. In other lineups there was no difference, making it very difficult to evaluate, with low detection rate and longer time to respond. In Table~\ref{tbl:model_result_demographics} notice that lineup specific error is estimated as 2.29 which is much higher than any of the other parameter estimates in the model. This indicates that the major and most important factor affecting the detection rate is  lineup difficulty.  So although the demographic factors emerge from the model to be statistically significant, the practical significance is minimal. We illustrate this with the following example of graduate degree.

@@

\begin{figure}[htbp] 
   \centering
%   \includegraphics[width=6.5in]{learning_trend.pdf} 
    \includegraphics[width=3.2in]{practical_impact_graduate.pdf} 
    \includegraphics[width=3.2in]{practical_impact_degree.pdf} 
   \caption{Proportion of estimated data identifications by an 18-25 year old female in the United States with a graduate degree compared to a high school degree. Even though having a graduate degree leads to  statistically significant increase, the effect size in the dependent variable is  0.045 which is  negligible from a practical point of view. The difference diminishes as we move away one or two standard deviations ($\sigma_{\ell} =2.29$) 
   of lineup variability.}
   \label{fig:practical_impact_graduate}
\end{figure}

@@

\begin{figure}[htbp] 
   \centering
    \includegraphics[width=6.5in]{proportion_nulls_guide.pdf} 
   \caption{Location of data plot in the lineup and proportion correct for both Interaction and Genotype effect. Each colored line represents a null set and the size of the dots represents number of responses. The overall average proportions are shown by dashed lines. The actual data plot locations are shaded grey on the top panels to demonstrate their relative positions on a lineup.}
   \label{fig:location_effect}
\end{figure}

>>>>

\begin{table}[hbtp]
\caption{Demographic information of the subjects participating in the MTurk experiments. Average time taken for evaluating a lineup is shown in seconds.}
\centering
\scalebox{.85}{
\begin{tabular}{rlrrcr}
  \hline
  && \multicolumn{2}{c}{Participants}&Average& Number of\\
  \cline{3-4}
 Factor & Levels & Total &\% & Time & Responses \\ 
  \hline
Gender & Female & 989 & 42.26 & 43.69 & 10538 \\ 
   & Male & 1351 & 57.74 & 48.75 & 13542 \\  
\hline
  Education & High school or less & 194 & 8.29 & 37.13 & 2253 \\ 
   & Under grad courses & 418 & 17.86 & 42.85 & 4068 \\ 
   & Under grad degree & 585 & 25.00 & 44.53 & 5792 \\ 
   & Graduate courses & 247 & 10.56 & 44.63 & 2471 \\ 
   & Graduate degree & 899 & 38.42 & 52.07 & 9496 \\ 
\hline
  Age & 18-25 & 743 & 31.75 & 43.50 & 7340 \\ 
   & 26-30 & 549 & 23.46 & 46.19 & 5610 \\ 
   & 31-35 & 375 & 16.03 & 44.19 & 3912 \\ 
   & 36-40 & 257 & 10.98 & 54.97 & 2714 \\ 
   & 41-45 & 140 & 5.98 & 43.89 & 1510 \\ 
   & 46-50 &  94 & 4.02 & 49.54 & 994 \\ 
   & above 50 & 184 & 7.86 & 52.32 & 2000 \\ 
\hline   
  Country & United States & 1086 & 46.41 & 39.65 & 10763 \\ 
   & India & 980 & 41.88 & 52.63 & 10238 \\ 
   & Rest of the world & 279 & 11.92 & 50.38 & 3079 \\

@@

% 
% % latex table generated in R 3.4.1 by xtable 1.8-2 package
% % Wed Oct 18 16:56:32 2017
% \begin{table}[ht]
% \centering
% \begin{tabular}{llrrrr}
%   \hline
% var & lbls & subsjects & percents & avg\_time & response \\ 
%   \hline
% gender\_level & Female & 989 & 42.26 & 43.69 & 10538 \\ 
%   gender\_level & Male & 1351 & 57.74 & 48.75 & 13542 \\ 
%   degree & High school or less & 194 & 8.29 & 37.13 & 2253 \\ 
%   degree & Under grad courses & 418 & 17.86 & 42.85 & 4068 \\ 
%   degree & Under grad degree & 585 & 25.00 & 44.53 & 5792 \\ 
%   degree & Graduate courses & 247 & 10.56 & 44.63 & 2471 \\ 
%   degree & Graduate degree & 899 & 38.42 & 52.07 & 9496 \\ 
%   age\_level & 18-25 & 743 & 31.75 & 43.50 & 7340 \\ 
%   age\_level & 26-30 & 549 & 23.46 & 46.19 & 5610 \\ 
%   age\_level & 31-35 & 375 & 16.03 & 44.19 & 3912 \\ 
%   age\_level & 36-40 & 257 & 10.98 & 54.97 & 2714 \\ 
%   age\_level & 41-45 & 140 & 5.98 & 43.89 & 1510 \\ 
%   age\_level & 46-50 &  94 & 4.02 & 49.54 & 994 \\ 
%   age\_level & above 50 & 184 & 7.86 & 52.32 & 2000 \\ 
%   country & United States & 1086 & 46.41 & 39.65 & 10763 \\ 
%   country & India & 980 & 41.88 & 52.63 & 10238 \\ 
%   country & Rest of the world & 279 & 11.92 & 50.38 & 3079 \\ 
%    \hline
% \end{tabular}
% \end{table}

@@

% latex table generated in R 3.4.1 by xtable 1.8-2 package
% Wed Oct 18 17:43:02 2017
\begin{table}[ht]
\caption{\label{tbl:anova_factor}Analysis of variance (ANOVA) table comparing full model, all the demographic factors, with the reduced models, obtained by removing respective factor variable. Gender does not have a significant effect on detection rate, but does on time to respond. All factors significantly affect time to respond.}
\centering
\scalebox{0.9}{
\begin{tabular}{lrrrrlrrrr}
& \multicolumn{4}{c} {Log Time (model~\ref{eqn:demographic_time})} & &\multicolumn{4}{c} {Detection rate (model~\ref{eqn:demographic_response})}  \\
\cline{2-5} \cline{7-10} 
 & Deviance & $\chi^2$ & df & $p$-value && Deviance & $\chi^2$ & df & $p$-value \\ \cline{2-5} \cline{7-10}
Full  & 52609.1 & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} &  & 24140.5 & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} & \multicolumn{1}{c}{---} \\ 
 - Age & 52081.3 & 527.8 & 6 & $<$0.001 & \hspace{0.5cm} & 24113.2 & 27.3 & 6 & $<$0.001 \\ 
 - Country & 52245.5 & 363.6 & 2 & $<$0.001 &  & 24114.8 & 25.7 & 2 & $<$0.001 \\ 
 - Degree & 52498.7 & 110.4 & 4 & $<$0.001 &  & 24116.0 & 24.5 & 4 & $<$0.001 \\ 
 - Gender & 52540.3 & 68.8 & 1 & $<$0.001 &  & 24138.9 & 1.6 & 1 & 0.200 \\ 
\cline{2-5} \cline{7-10}
\end{tabular}}
\end{table}

% % latex table generated in R 3.4.1 by xtable 1.8-2 package
% % Wed Oct 18 17:43:02 2017
% \begin{table}[ht]
% \centering
% \begin{tabular}{rrrrrlrrrr}
%   \hline
%  & deviance & Chisq & Chi.Df & Pr..Chisq. & g1 & deviance & Chisq & Chi.Df & Pr..Chisq. \\ 
%   \hline
% Full & 52609.06 & 0.00 & 6.00 & 0.00 &  & 24140.49 & 0.00 & 6.00 & 0.00 \\ 
%   Age & 52081.29 & 527.77 & 6.00 & 0.00 &  & 24113.24 & 27.25 & 6.00 & 0.00 \\ 
%   Country & 52245.46 & 363.60 & 2.00 & 0.00 &  & 24114.79 & 25.70 & 2.00 & 0.00 \\ 
%   Degree & 52498.65 & 110.41 & 4.00 & 0.00 &  & 24116.02 & 24.47 & 4.00 & 0.00 \\ 
%   Gender & 52540.30 & 68.76 & 1.00 & 0.00 &  & 24138.85 & 1.64 & 1.00 & 0.20 \\ 
%    \hline
% \end{tabular}
% \end{table}

@@

% latex table generated in R 3.4.1 by xtable 1.8-2 package
% Wed Oct 18 17:22:24 2017
\begin{table}[hbtp]
\caption{\label{tbl:model_result_demographics}Parameter estimates of models~\eqref{eqn:demographic_time} and~\eqref{eqn:demographic_response} fitted for average log time taken and detection rate, respectively. For time taken all the demographic factors are significant. For detection rate, age group 36-40, rest of the world and graduate degree are significantly different. For gender no difference in performance is observed. Lineup variability is estimated to be very large for model~\eqref{eqn:demographic_response}.}
\centering
\scalebox{.9}{
\begin{tabular}{rrr>{(}r<{,}>{\hspace{-.1in}}l<{)}>{\hspace{-.15in}}l<{}cr>{(}r<{,}>{\hspace{-.1in}}l<{)}>{\hspace{-.15in}}l<{}}
 && \multicolumn{4}{c} {Log Time (model~\ref{eqn:demographic_time})} & &\multicolumn{4}{c} {Detection rate (model~\ref{eqn:demographic_response})}  \\

\cline{3-6} \cline{8-11} 
\multicolumn{2}{c}{{Demographic Factor} \hfill Level} & Est & 2.5\% & 97.5\% &   && Est & 2.5\% & 97.5\% &   \\ 
\cline{3-6} \cline{8-11}
\bf Fixed Effects & Average $\mu$ & 3.16 & 3.12 & 3.20 & *** &   & -0.63 & -0.81 & -0.45 & *** \\ [3pt]
\bf Age Category $(\alpha)$ & 18-25 & \multicolumn{5}{l}{0.00} & \multicolumn{4}{l}{\phantom{-}0.00} \\
&  26-30 & 0.05 & 0.03 & 0.07 & *** &   & 0.03 & -0.06 & 0.13 &  \\ 
&  31-35 & 0.06 & 0.03 & 0.09 & *** &   & 0.12 & 0.02 & 0.23 & * \\ 
&  36-40 & 0.22 & 0.19 & 0.25 & *** &   & 0.29 & 0.17 & 0.41 & *** \\ 
&  41-45 & 0.17 & 0.13 & 0.21 & *** &   & 0.19 & 0.03 & 0.34 & * \\ 
&  46-50 & 0.28 & 0.23 & 0.32 & *** &   & 0.20 & 0.01 & 0.39 & * \\ 
&  above 50 & 0.34 & 0.31 & 0.38 & *** &   & 0.16 & 0.02 & 0.29 & * \\ [3pt]
\bf Country $(\kappa)$& U.S. & \multicolumn{5}{l}{0.00} & \multicolumn{4}{l}{\phantom{-}0.00} \\
&  India & 0.23 & 0.20 & 0.25 & *** &   & -0.19 & -0.28 & -0.10 & *** \\ 
&  Rest of the world & 0.14 & 0.11 & 0.17 & *** &   & 0.06 & -0.05 & 0.18 &  \\ [3pt]
\bf Education $(\tau)$& High School & \multicolumn{5}{l}{0.00} & \multicolumn{4}{l}{\phantom{-}0.00} \\
&  Under grad courses & 0.13 & 0.09 & 0.16 & *** &   & 0.00 & -0.14 & 0.14 &  \\ 
&  Under grad degree & 0.14 & 0.10 & 0.17 & *** &   & 0.16 & 0.03 & 0.29 & * \\ 
&  Graduate courses & 0.02 & -0.02 & 0.06 &  &   & -0.13 & -0.29 & 0.03 &  \\ 
&  Graduate degree & 0.13 & 0.10 & 0.16 & *** &   & -0.04 & -0.17 & 0.09 &  \\ [3pt]
\bf Gender $(\gamma)$& Female & \multicolumn{5}{l}{0.00} & \multicolumn{4}{l}{\phantom{-}0.00} \\
&  Male & 0.08 & 0.06 & 0.10 & *** &   & 0.05 & -0.02 & 0.12 &  \\
\cline{3-6} \cline{8-11}
\bf Random Effects &  lineup $(\sigma_\ell)$& \multicolumn{5}{l}{0.29} & \multicolumn{4}{l}{\phantom{-}2.27} \\ 
                   &  Error $(\sigma)$& \multicolumn{5}{l}{0.69} & \multicolumn{4}{l}{\phantom{-}0.89}  \\ 
\cline{3-6} \cline{8-11}\\
\hline
\multicolumn{10}{l}{Signif. codes:  *** $<$ 0.001 $\le$ ** $<$ 0.01 $\le$ * $<$ 0.05 $\le$ . $<$ 0.1 $\le$ ` ' $<$ 1}
\end{tabular}}
\end{table}

% % latex table generated in R 3.4.1 by xtable 1.8-2 package
% % Wed Oct 18 17:22:24 2017
% \begin{table}[ht]
% \centering
% \begin{tabular}{rrrrllrrrl}
%   \hline
%  & Est & LB & UB & pvalue & g1 & Est & LB & UB & pvalue \\ 
%   \hline
% $\mu$ & 3.16 & 3.12 & 3.20 & *** &   & -0.63 & -0.81 & -0.45 & *** \\ 
%   26-30 & 0.05 & 0.03 & 0.07 & *** &   & 0.03 & -0.06 & 0.13 &  \\ 
%   31-35 & 0.06 & 0.03 & 0.09 & *** &   & 0.12 & 0.02 & 0.23 & * \\ 
%   36-40 & 0.22 & 0.19 & 0.25 & *** &   & 0.29 & 0.17 & 0.41 & *** \\ 
%   41-45 & 0.17 & 0.13 & 0.21 & *** &   & 0.19 & 0.03 & 0.34 & * \\ 
%   46-50 & 0.28 & 0.23 & 0.32 & *** &   & 0.20 & 0.01 & 0.39 & * \\ 
%   above 50 & 0.34 & 0.31 & 0.38 & *** &   & 0.16 & 0.02 & 0.29 & * \\ 
%   India & 0.23 & 0.20 & 0.25 & *** &   & -0.19 & -0.28 & -0.10 & *** \\ 
%   Rest of the world & 0.14 & 0.11 & 0.17 & *** &   & 0.06 & -0.05 & 0.18 &  \\ 
%   Under grad courses & 0.13 & 0.09 & 0.16 & *** &   & 0.00 & -0.14 & 0.14 &  \\ 
%   Under grad degree & 0.14 & 0.10 & 0.17 & *** &   & 0.16 & 0.03 & 0.29 & * \\ 
%   Graduate courses & 0.02 & -0.02 & 0.06 &  &   & -0.13 & -0.29 & 0.03 &  \\ 
%   Graduate degree & 0.13 & 0.10 & 0.16 & *** &   & -0.04 & -0.17 & 0.09 &  \\ 
%   Male & 0.08 & 0.06 & 0.10 & *** &   & 0.05 & -0.02 & 0.12 &  \\ 
%   lineup & 0.29 &  &  &  &   & 2.27 &  &  &  \\ 
%    \hline
% \end{tabular}
% \end{table}

@@

Figure~\ref{fig:demographic_effect} supports the model results. The average time taken to respond (natural log) and detection rate are computed by lineup for the different demographic factor levels, and displayed using boxplots. Mean values are shown as dots inside the boxplot, as this statistic rather than the median is used in the models. %There are some small differences across demographic groups. The youngest age group (18-25) took least average time to evaluate a lineup. People from India took more time than others. People who have only a high school degree took less time and this is related to what we have seen for young age group. Averages of log time taken by male and female participants look similar but there are some differences as we see in Table~\ref{tbl:demographics}. 
The means and medians for response time (top row) are essentially equal. There are some differences between the two in the detection rate plots (bottom row). The differences in these values for different factors, that was tested by the models, can be seen in the plots. However, particularly for detection rate, the variation is huge. A large component of the variation is difficulty of the lineup. In some lineups the actual data plot was distinctively different from the null plots, and we would expect that the detection rate would be close to 100\%. In other lineups there was no difference, making it very difficult to evaluate, with low detection rate and longer time to respond. In Table~\ref{tbl:model_result_demographics} notice that lineup specific error is estimated as 2.27 which is much higher than any of the other parameter estimates in the model. This indicates that the major and most important factor affecting the detection rate is  lineup difficulty.  So although the demographic factors emerge from the model to be statistically significant, the practical significance is minimal. We illustrate this with the following example of graduate degree.

@@

\begin{figure}[htbp] 
   \centering
%   \includegraphics[width=6.5in]{learning_trend.pdf} 
    \includegraphics[width=3.2in]{practical_impact_graduate.pdf} 
    \includegraphics[width=3.2in]{practical_impact_degree.pdf} 
   \caption{Proportion of estimated data identifications by an 18-25 year old female in the United States with a graduate degree compared to a high school degree. Even though having a graduate degree leads to  statistically significant increase, the effect size in the dependent variable is  0.045 which is  negligible from a practical point of view. The difference diminishes as we move away one or two standard deviations ($\sigma_{\ell} =2.27$) 
   of lineup variability.}
   \label{fig:practical_impact_graduate}
\end{figure}

@@

\begin{figure}[htbp] 
   \centering
    \includegraphics[width=6.5in]{proportion_nulls_guide.pdf} 
   \caption{Location of data plot in the lineup and proportion correct (detection rate) for both Interaction and Genotype effect. Each colored line represents a null set and the size of the dots represents number of responses. The overall average proportions are shown by dashed lines. The actual data plot locations are shaded grey on the top panels to demonstrate their relative positions on a lineup.}
   \label{fig:location_effect}
\end{figure}
